---
title: "What the package does"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{What the package does}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4573NGUY24)
```

# Introduction

Below are a set of functions and one dataset

The following functions are a list of functions made throughout this course that were put in the course' package. 

## Function 1: myplot()

* This function takes values in the form of x and returns heights. The returned value is used to make quadratic plots

```{r}
myplot(32)
```



## Function 2 myncurve()

myncurve() takes in probability, mean, and standard deviation and returns the probability density that the value of a variable that follows the standard normal distribution is equal to x

```{r}
myncurve(mu=10,sigma=5, a=6)
```


## Function 3 mycltb()

mycltb() takes in sample size, # of iterations, and probability and returns a histogram plot of a binomial

```{r}
mycltb(n=20,iter=10000,p=0.5)
```


## Function 4: mymlnorm()

mymlnorm() takes in population vector, mean of population vector, and standard deviation of population vector and returns a plot of the maximum likelihood estimates for the population mean and standard deviation

```{r}
mymlnorm(x=c(10,10,11,12,12,13,16,15,15),mu=seq(10,15,length=1000),sig=seq(0.1,4,length=1000),lwd=2,labcex=1)
```


## Data Set: FIREDAM

FIREDAM is data set representing a sample of 15 recent fires in  a large suburb of a major city is selected. The amount of damage y and the distance x between the fire and the nearest fire station are recorded for each fire.

```{r}
data("fire")
knitr::kable(fire)
```





